Analysis of residual plot model

### 2023-10-09 scripts/evaluation/experiment_factor.Rmd
update training script

```{r set_global_variables}
ALL_RES <- c(32L, 64L)
```

@@

```{r basic_summary}

basic_summary <- function(dat, res = 32L) {
  dat %>%
  ggplot() +
  geom_bar(aes(pred, fill = type), position = "dodge") +
  geom_text(data = dat %>%
              group_by(truth, type, pred) %>%
              summarise(prop = n()/2000) %>%
              filter(type == "heteroskedasticity"),
  aes(pred, prop * 2000, label = format(prop, digits = 3)),
  nudge_x = -0.25, nudge_y = 30) +
  geom_text(data = dat %>%
              group_by(truth, type, pred) %>%
              summarise(prop = n()/2000) %>%
              filter(type == "polynomial"),
  aes(pred, prop * 2000, label = format(prop, digits = 3)),
  nudge_x = 0.25, nudge_y = 30) +
  xlab("Prediction") +
  theme_light() +
  facet_wrap(~truth, labeller = label_both) +
  ylab("Count") +
  scale_fill_brewer(palette = "Set2") +
  ggtitle("Summary of prediction", subtitle = glue("Image size {res} * {res}"))
}

for (res in ALL_RES) {
  print(basic_summary(pred[[res]], res))
}

```

@@

>>>>

```{r set_global_variables}
ALL_RES <- c(32L, 64L, 128L)
```

@@

```{r}
pred %>%
  reduce(bind_rows) %>%
  group_by(res, truth, type, pred) %>%
  summarise(prop = n()/2000)  %>%
  filter(truth == pred) %>%
  select(-pred) %>%
  pivot_wider(names_from = truth, values_from = prop) %>%
  arrange(type, res) %>%
  kableExtra::kable(col.names = c("Input size", "Violation", "Accuracy: not_null", "Accuracy: null")) %>%
  kableExtra::kable_material()
```

@@

# ROC

```{r roc}
pred %>%
  reduce(bind_rows) %>%
  group_by(res) %>%
  roc_curve(truth, V1) %>%
  autoplot() +
  labs(col = "Input size") +
  ggtitle("ROC")
```

# Distribution of predicted probability

```{r p_hat_distribution}
p_hat_distribution <- function(dat, res = 32) {
  dat %>%
    ggplot() +
    geom_histogram(aes(V1)) +
    ggtitle(quote("Distribution of " ~ hat(P)(y == not_null) ~ "on the test set"), 
            subtitle = glue("Input size {res} * {res}")) +
    xlab(quote(hat(P)(y == not_null))) +
    facet_grid(type ~ truth, labeller = label_both) +
    theme_light()
}

for (res in ALL_RES) {
  p_hat_distribution(pred[[res]], res) %>%
    print()
}
```

# Distribution of predicted probability on null set

```{r p_hat_null_shape}
p_hat_null_shape <- function(dat, res = 32) {
  dat %>%
    filter(truth == "null") %>%
    ggplot() +
    geom_boxplot(aes(factor(x_dist), V1)) +
    ylab(quote(hat(P)(y == not_null))) +
    xlab("Distribution of fitted values") +
    scale_x_discrete(labels = c("discrete uniform", "lognormal", "normal", "uniform")) +
    ggtitle(quote("Distribution of " ~ hat(P)(y == not_null ~"|"~ truth == null) ~ "on the test set"), 
            subtitle = glue("Input size {res} * {res}")) +
    theme_light()
}

for (res in ALL_RES) {
  p_hat_null_shape(pred[[res]], res) %>%
    print()
}
```
